Orientation Control System: Enhancing Aerial Maneuvers for Quadruped Robots

### 2023-01-04 mdpi2022roscia.tex
references update

\section{Background}
\label{sec:background}
The starting point for any \gls{ocs} is the Euler's equation. For any mechanical system, the time derivative of the angular momentum $\bm{L}$ computed with the respect to a reference point $O$, fixed in an inertial frame, equals the sum of the moments $\bm{M}_i$ applied to the system with respect to the same reference point:
\begin{equation}
\dot{\bm{L}} = \sum_i \bm{M}_i
\end{equation}
When the resultant of the external moments applied to the system is zero, the Euler's equation simplifies to:
\begin{equation}
\dot{\bm{L}} = 0 \quad \Rightarrow \quad \bm{L}(t) = const,
\label{eq:cons_ang_mom}
\end{equation}
which is known as conservation of angular momentum.
Referring to legged robots, this condition occurs when the system is not in contact with the ground or other objects, e.g., during a fall or the flight phase of a jump.
In this case, it is possible to change the angular velocity of the base link changing the joint positions and velocities, as a result of the \textit{non-holonomy} of the total angular momentum \cite{Wieber16}: if the angular momentum of a certain body changes, the one of the others must change to maintain the total sum constant.
\subsection{Preliminary Analysis}
Most of quadruped robots are designed in such a way that the largest amount of the mass is located at the main body. As a consequence, the contribution of the moments due to the acceleration of other bodies (i.e. leg links) is moderate. \\
As an example, let consider the case of Solo12. Even if each limb accounts for about $13.4\%$ of the total mass, changes of the total robot inertia come with the motion of only the upperleg (thigh) and the lowerleg (calf), since the displacement of distribution of the hip mass with the system \acrshort{com} is approximately constant. \MF{In view of this, each limb is responsible for only $7.5\%$ of the total mass to vary the total inertia of the robot}. Flywheels can be used for alleviating the lack of control authority.

>>>>

\section{Background}
\label{sec:background}
The starting point for any \gls{ocs} is the Euler's equation. For any mechanical system, the time derivative of the angular momentum $\bm{L}$ computed with the respect to a reference point $O$, fixed in an inertial frame, equals the sum of the moments $\bm{M}_i$ applied to the system with respect to the same reference point:
\begin{equation}
\dot{\bm{L}} = \sum_i \bm{M}_i
\end{equation}
When the resultant of the external moments applied to the system is zero, the Euler's equation simplifies to:
\begin{equation}
\dot{\bm{L}} = 0 \quad \Rightarrow \quad \bm{L}(t) = const,
\label{eq:cons_ang_mom}
\end{equation}
which is known as conservation of angular momentum.
Referring to legged robots, this condition occurs when the system is not in contact with the ground or other objects, e.g., during a fall or the flight phase of a jump.
In this case, it is possible to change the angular velocity of the base link changing the joint positions and velocities, as a result of the \textit{non-holonomy} of the total angular momentum \cite{wieber2016modeling}: if the angular momentum of a certain body changes, the one of the others must change to maintain the total sum constant.
\subsection{Preliminary Analysis}
Most of quadruped robots are designed in such a way that the largest amount of the mass is located at the main body. As a consequence, the contribution of the moments due to the acceleration of other bodies (i.e. leg links) is moderate. \\
As an example, let consider the case of Solo12. Even if each limb accounts for about $13.4\%$ of the total mass, changes of the total robot inertia come with the motion of only the upperleg (thigh) and the lowerleg (calf), since the displacement of distribution of the hip mass with the system \acrshort{com} is approximately constant. \MF{In view of this, each limb is responsible for only $7.5\%$ of the total mass to vary the total inertia of the robot}. Flywheels can be used for alleviating the lack of control authority.
